% !TeX root = ../dd.tex
In this section the requirements specified in the RASD are mapped to the components defined above. For brevity,
the API Gateway is omitted as, since it mediates most of the operations, it would need to be specified in almost
all requirements.
\begin{center}
    \begin{longtable}{|l|p{8cm}|p{5cm}|}
        \hline
              & \textbf{Description}                                                                                                                                                           & \textbf{Components}                                                        \\\hline
        \hline
        \endhead
        \hline
        \endfoot
        \hline
        \caption{Components traceability matrix}
        \label{table:Components traceability matrix}
        \endlastfoot
        R1    & The system shall allow users to log in with SSO.                                                                                                                               & \textbf{User Service}                                                      \\\hline
        R2    & The system shall allow the educator to create a tournament.                                                                                                                    & \textbf{Platform Service}                                                  \\\hline
        R2.1  & The system shall allow the educator to specify the subscription deadline of a tournament.                                                                                      & \textbf{Platform Service}                                                  \\\hline
        R2.2  & The system shall allow the educator to grant other colleagues the permission to create battles within the context of a specific tournament.                                    & \textbf{User Service, Platform Service}                                    \\\hline
        R2.3  & The system shall notify the students of the new tournament.                                                                                                                    & \textbf{Platform Service, Notification Service}                            \\\hline
        R2.4  & The system shall allow the educator who create the tournament to close it.                                                                                                     & \textbf{Platform Service}                                                  \\\hline
        R3    & The system shall allow students to subscribe to a tournament.                                                                                                                  & \textbf{Platform Service}                                                  \\\hline
        R4    & The system shall allow the educator to create a battle within the context of a specific tournament.                                                                            & \textbf{Platform Service}                                                  \\\hline
        R4.1  & The system shall allow the educator to set minimum and maximum number of students per group.                                                                                   & \textbf{Platform Service}                                                  \\\hline
        R4.2  & The system shall allow the educator to set a textual description.                                                                                                              & \textbf{Platform Service}                                                  \\\hline
        R4.3  & The system shall allow the educator to set the programming language.                                                                                                           & \textbf{Platform Service}                                                  \\\hline
        R4.4  & The system shall allow the educator to upload a set of test cases.                                                                                                             & \textbf{Platform Service, Build and Test Service}                          \\\hline
        R4.5  & The system shall allow the educator to upload a build automation script.                                                                                                       & \textbf{Platform Service, Build and Test Service}                          \\\hline
        R4.6  & The system shall allow the educator to set a registration deadline.                                                                                                            & \textbf{Platform Service}                                                  \\\hline
        R4.7  & The system shall allow the educator to set a final submission deadline.                                                                                                        & \textbf{Platform Service}                                                  \\\hline
        R4.8  & The system shall allow the educator to enable manual evaluation.                                                                                                               & \textbf{Platform Service}                                                  \\\hline
        R4.9  & The system shall allow the educator to select aspects that should be evaluated by the static analysis tool, such as security, reliability, and maintainability.                & \textbf{Platform Service, Static Analysis Service}                         \\\hline
        R4.10 & The system shall notify students subscribed to a tournament of the creation of a new battle.                                                                                   & \textbf{Platform Service, Notification Service}                            \\\hline
        R5    & The system shall allow students to join a battle, respecting the minimum and maximum number of students per group.                                                             & \textbf{Platform Service}                                                  \\\hline
        R5.1  & The system shall allow students to invite other students to join a battle.                                                                                                     & \textbf{Platform Service, User Service}                                    \\\hline
        R5.2  & The system shall allow students to accept received invitation.                                                                                                                 & \textbf{Platform Service}                                                  \\\hline
        R6    & When the registration deadline expires, the system shall create a GitHub repository containing the code kata.                                                                  & \textbf{Platform Service}                                                  \\\hline
        R7    & The system shall send the link to all students who are members of subscribed teams.                                                                                            & \textbf{Notification Service}                                              \\\hline
        R8    & The system shall expose an API that can by called by the GitHub Action platform.                                                                                               & \textbf{API Gateway}                                                       \\\hline
        R9    & On each push, the system shall calculate and update the battle score of the team.                                                                                              & \textbf{Platform Service, Build and Test Service, Static Analysis Service} \\\hline
        R9.1  & The system shall pull the latest sources.                                                                                                                                      & \textbf{Build and Test Service}                                            \\\hline
        R9.2  & The system shall analyze quality level of the sources, based on the aspect selected by the educator.                                                                           & \textbf{Static Analysis Service}                                           \\\hline
        R9.3  & The system shall run tests uploaded by the educator.                                                                                                                           & \textbf{Build and Test Service}                                            \\\hline
        R9.4  & The system shall measure the time passed between the registration deadline and the last commit.                                                                                & \textbf{Platform Service}                                                  \\\hline
        R10   & The system shall allow students and educators involved in the battle to see the current rank evolving during the battle.                                                       & \textbf{Platform Service}                                                  \\\hline
        R11   & When the submission deadline expires, if manual evaluation is required, the system shall change the state of the battle to the consolidation stage.                            & \textbf{Platform Service}                                                  \\\hline
        R12   & When the submission deadline expires, if manual evaluation is not required, the system shall close the battle.                                                                 & \textbf{Platform Service}                                                  \\\hline
        R13   & During the consolidation stage, if manual evaluation is required, the system shall allow the educator to go through the sources produced by each team to assign his/her score. & \textbf{Platform Service}                                                  \\\hline
        R14   & At the end of a battle, the system shall calculate the final rank.                                                                                                             & \textbf{Platform Service}                                                  \\\hline
        R15   & When the final rank is available, the system shall notify all students participating in the battle.                                                                            & \textbf{Platform Service, Notification Service}                            \\\hline
        R16   & At the end of each battle, the platform updates the personal tournament score of each student, that is the sum of all battle scores received in that tournament.               & \textbf{Platform Service}                                                  \\\hline
        R17   & The system shall allow users to see the tournament ranks.                                                                                                                      & \textbf{Platform Service}                                                  \\\hline
        R18   & At the end of a tournament, the system shall calculate the final tournament rank.                                                                                              & \textbf{Platform Service}                                                  \\\hline
        R19   & When the final tournament rank is available, the system shall notify all students involved in the tournament.                                                                  & \textbf{Platform Service, Notification Service}                            \\\hline
        R20   & The system shall allow the educator who create a tournament, to create badges within the context of the tournament.                                                            & \textbf{Platform Service, Badge Service}                                   \\\hline
        R20.1 & The system shall allow the educator to specify the title of the badge.                                                                                                         & \textbf{Badge Service}                                                     \\\hline
        R20.2 & The system shall allow the educator to create a new variable that represent any piece of information available in the platform relevant for scoring.                           & \textbf{Badge Service}                                                     \\\hline
        R20.3 & The system shall allow the educator to specify one or more rules that must be fulfilled to achieve the badge, based on variables.                                              & \textbf{Badge Service}                                                     \\\hline
        R20.4 & The system shall allow users to visualize badges collected by a student.                                                                                                       & \textbf{Badge Service}                                                     \\\hline
        R21   & At the end of a tournament, the system shall assign badges to the student who fulfilled the rules.                                                                             & \textbf{Badge Service}                                                     \\\hline
    \end{longtable}
\end{center}
